Supporting Information:\\ NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-12-10 Manuscript/manuscriptPS.tex
Update simulation detilas

    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04} &0    & 0   & 102:26 & 4290 & 0   & 310  & 80 & 120 & \cite{bergerPOPSPOPC4:1mixtureT310K}  \\
    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04}\todoi{Are these correct references?} &1.03    & 0   & 102:26 & 4290 & 80  & 310  & 200 & 50 & \cite{POPCpopsBERGERwith1000mMNa}  \\

>>>>

    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04} &0    & 0   & 102:26 & 4290 & 0   & 310  & 120 & 80 & \cite{bergerPOPSPOPC4:1mixtureT310K}  \\
    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04} &1.03    & 0   & 102:26 & 4290 & 80  & 310  & 200 & 50 & \cite{POPCpopsBERGERwith1000mMNa}  \\

### 2018-12-10 Manuscript/manuscriptPSsuppl.tex
Update simulation detilas

\noindent
{\it POPC:POPS (5:1) mixtures with additional monovalent ions} \\
POPC:POPS (5:1) mixtures containing total 132 (110:22) lipids
were simulated with the additional potassium and sodium countertion concentrations
of $\sim$450 mM and 890 mM using CHARMM36 force field at 298 K. The data, force field and
input files generated using parameters given by CHARMM-GUI \cite{lee16,jo18} are
available from Refs. \citenum{charmm36pops+83popcT298Kwith450mMK,charmm36pops+83popcT298Kwith890mMK,charmm36pops+83popcT298Kwith440mMNa,charmm36pops+83popcT298Kwith890mMNa}. \\

@@

\subsection{MacRog}
\noindent
{\it POPC bilayers.} \\

@@

\subsection{Berger}
\noindent
{\it POPC bilayers.} \\
Previously published simulation of POPC at 310 K \cite{ollila07a}, available from Ref. \cite{bergerPOPC310K},
was used.

@@

\noindent
{\it POPC:POPS (4:1) mixtures with additional sodium and calcium ions} \\
Simulations with excess sodium were taken directly from Ref. \citenum{jurkiewicz12} and
simulations with calcium directly from \citenum{melcrova16}.

\subsection{Slipids}
\todo{To be written by Piggot and Favela}

\subsection{GROMOS-CKP}
\todo{To be written by Piggot}
  CKPM refers to the version with Berger/Chiu NH$_3$ charges compatible with Berger
   (i.e. the NH$_3$ group having the same charges as in the N(CH$_3$)$_3$ group of the PC lipids;
   'M' stands for Mukhopadhyay after the first published Berger-based PS simulation that used these charges~\cite{mukhopadhyay04})
   and CKP refers to the version with more Gromos compatible version
   (i.e. the charges for the NH$_3$ group taken from the lysine side-chain).

>>>>

\noindent
{\it POPC:POPS (5:1) mixtures with additional monovalent ions.}
Systems containing total 132 (110:22) lipids
were simulated with the additional potassium and sodium countertion concentrations
of $\sim$450 mM and 890 mM using CHARMM36 force field at 298 K. The data, force field and
input files generated using parameters given by CHARMM-GUI \cite{lee16,jo18} are
available from Refs. \citenum{charmm36pops+83popcT298Kwith450mMK,charmm36pops+83popcT298Kwith890mMK,charmm36pops+83popcT298Kwith440mMNa,charmm36pops+83popcT298Kwith890mMNa}. \\

@@

\subsection{MacRog}
\noindent
    {\it POPC bilayers.} Simulation data available from Ref. \citenum{macrogPOPC298K}.
    \todo{For example this data set has pretty good description of simulation details in the
      reference. I am not sure how much we should repeat these in here.}

@@

\subsection{Berger}
\noindent
{\it POPC bilayers.} 
Previously published simulation \cite{ollila07a} available from Ref. \citenum{bergerPOPC310K}
was used for POPC at 310 K.

@@

\noindent
{\it POPC:POPS (4:1) mixtures with additional sodium and calcium ions.} 
Previously published simulations with the additional amount of sodium \cite{jurkiewicz12}
available from Ref. \citenum{POPCpopsBERGERwith1000mMNa} and with the additional amounts
of calcium \cite{melcrova16} available from Refs. \citenum{POPCpopsBERGERwith102mMCa,POPCpopsBERGERwith715mMCa}
were used. The additional sodium ions were removed from the structure file of the simulation
with excess amount of sodium \cite{POPCpopsBERGERwith1000mMNa} to generate the initial structure for the reference simulation
with sodium counterions only. The data, input and force field parameter files of the reference simulation
are available from Ref. \citenum{bergerPOPSPOPC4:1mixtureT310K}. \todo{The simulation details of this are
  not clearly described in Zenodo repository, but can be read from the mdp file available there. Should we
write the detailes here or not?}

\subsection{GROMOS-CKP and GROMOS-CKPM}
  CKPM refers to the version with Berger/Chiu NH$_3$ charges compatible with Berger
   (i.e. the NH$_3$ group having the same charges as in the N(CH$_3$)$_3$ group of the PC lipids;
   'M' stands for Mukhopadhyay after the first published Berger-based PS simulation that used these charges~\cite{mukhopadhyay04})
   and CKP refers to the version with more Gromos compatible version
   (i.e. the charges for the NH$_3$ group taken from the lysine side-chain).
\todo{T. Piggot, please write the description of force field.}

\noindent
{\it DOPS and POPS bilayers.} \\
The data in Table \ref{PSsystems} and Refs. \citenum{ckp1POPS303K,ckp2POPS303K,ckp1DOPS303K,ckp2DOPS303K}
\todo{T. Piggot, please write simulation details} \\

\noindent
    {\it POPC:POPS (5:1) mixtures without additional ions}\\
    The data in Table \ref{mixedIONsystems} and Refs. \citenum{POPCpopsGROMOSCKPwithNa,POPCpopsGROMOSCKPMwithNa}
\todo{T. Piggot, please write simulation details} \\

\subsection{Slipids}

\noindent
{\it DOPS and POPS bilayers.} \\
The data in Table \ref{PSsystems} and Refs. \citenum{slipidsPOPS298K,slipidsDOPS303K,slipidsDOPSfiles}.
\todo{T. Piggot and F. Favela, please write simulation details} \\
